---
title: Co Occurrence of Characters in Les Miserable
author: Emil Hvitfeldt
date: '2018-02-23'
slug: co-occurrence-of-characters-in-les-miserable
categories:
  - R
tags:
  - NLP
  - cleanNLP
  - tidyverse
  - ggplot2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## What are we doing?

The inspiration for this post is [this beutiful vizualization](https://bost.ocks.org/mike/miserables/) from [Mike Bostock](https://bost.ocks.org/mike/). It nicely vizualizes the co-occurence of characters (when two characters appear in the same chapter) in the novel [Les Misérables](https://en.wikipedia.org/wiki/Les_Mis%C3%A9rables) by [Victor Hugo](https://en.wikipedia.org/wiki/Victor_Hugo) using the data collected by [Jacques Bertin](https://en.wikipedia.org/wiki/Jacques_Bertin) (and his assistants).  

The way this post will differentiate itself from this is that we are going to collect the data ourselves using [named entity recognition](https://en.wikipedia.org/wiki/Named-entity_recognition). Named entity recognition is the dicipline of location and classifying named entities in text. Furthermore will we also try to cluster the characters according to their appearence in the novel. 

## Loading package

for this we will need `tidyverse` for general data science tasks, `cleanNLP` for the named entity recognition and `igraph` for some graph related transformation.

```{r, message=FALSE}
library(tidyverse)
library(cleanNLP)
library(igraph)
```
